Improvement of crash forces in structures using optimization tools.

### 2016-07-28 paper.tex
Avances

\Cref{fig:car,fig:plane} show the schematics of a car frame and a fuselage section, both enclosing crash boxes. In this research, a finite element model of an adhesive-bonded energy absorber subjected to impact loads is studied. The specimen is defined and optimized according to crashworthiness metrics in order to better its performance as a crashworthy element. Information and data present in the literature are used to create and validate these models in order to ensure the accuracy of the results.

@@

\section{Conclusions}
From this research the following conclusions can be drawn:
\begin{itemize}
	\item The crash behavior of adhesively bonded steel crash boxes have been successfully simulated in a commercial finite element package. Results have been validated with experimental data in the literature.
	\item A description of a suitable optimization method for the analyzed crash boxes is provided. A multiobjective algorithm enables the balancing of contrasting objective functions like the specific energy absorption and the peak loads of the structures.
\end{itemize}

>>>>

\Cref{fig:car,fig:plane} show the schematics of a car frame and a fuselage section, both enclosing crash boxes. In this research, a finite element model of an adhesive-bonded energy absorber subjected to impact loads is studied. The specimen is analyzed and its optimization is proposed according to crashworthiness metrics in order to better its performance as a crashworthy element. Information and data present in the literature are used to create and validate these models in order to ensure the accuracy of the results.

@@

\section{Conclusions}
From this research the following conclusions can be drawn:
\begin{itemize}
	\item The crash behavior of adhesively bonded steel crash boxes have been successfully simulated in a commercial finite element package.
	\item Results have been validated with experimental data in the literature.
	\item A description of a suitable optimization method for the analyzed crash boxes is provided. A multiobjective algorithm enables the balancing of contrasting objective functions like the specific energy absorption and the peak loads of the structures.
\end{itemize}
